---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# paracorp

<!-- badges: start -->
[![R-CMD-check](https://github.com/gederajeg/paracorp/workflows/R-CMD-check/badge.svg)](https://github.com/gederajeg/paracorp/actions)
[![Codecov test coverage](https://codecov.io/gh/gederajeg/paracorp/branch/main/graph/badge.svg)](https://app.codecov.io/gh/gederajeg/paracorp?branch=main)
[![](https://img.shields.io/badge/doi-10.17605/OSF.IO/HV9CU-lightblue.svg)](https://doi.org/10.17605/OSF.IO/HV9CU)
<!-- badges: end -->

The goal of **paracorp** is to provide an R functionality for generating parallel concordance (Keyword-in-Context [KWIC] display) from a parallel/bilingual corpora. The first attempt is implemented in the `para_conc()` function that is built on top of the [tidyverse](https://www.tidyverse.org/) suit of packages. Please use the following citation if **paracorp** is used in publications:

```{r how-to-cite}
citation("paracorp")
```


The **paracorp** package is part of the following [research project](https://udayananetworking.unud.ac.id/lecturer/research/880-gede-primahadi-wijaya-rajeg/a-model-for-translation-study-based-on-english-indonesian-translation-database-and-its-pedagogical-implication-1179):

> Rajeg, Gede Primahadi Wijaya, I Made Rajeg, Putu Dea Indah Kartini & I Gede Semara Dharma Putra. 2021. Material pendukung untuk *MODEL KAJIAN TERJEMAHAN BERBASIS BANK DATA TERJEMAHAN DIGITAL INGGRIS-INDONESIA DAN IMPLIKASI PEDAGOGISNYA*. Open Science Framework. https://doi.org/10.17605/OSF.IO/Y6ESA. https://osf.io/y6esa/.

## Installation

You can install the development version of paracorp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gederajeg/paracorp")
```

## Example

The **paracorp** package comes with internal sample data of English-Indonesian parallel corpora from the science genre developed by the PAN BPPT project [citation]. The data are available in the form of character vectors called `sci_en` (for the English text) whose line is aligned with the Indonesian version (`sci_id`).

The codes below shows how to generate a parallel concordance for the English modal verb "should" as the target, search-term and present the Indonesian translation (shown in the `TRANSLATION` column in the output table).

```{r example-eng-idn}
library(paracorp) # load the package

# in this example, the English text is used as the source text
my_para_conc <- para_conc(source_text = sci_en, 
                          target_text = sci_id, 
                          pattern = "\\bshould\\b", # regular expression pattern
                          conc_sample = 20) # retrieve 20 random concordance lines
head(my_para_conc)

```

The printed messages show that, by default, `para_conc()` also saves the concordance into a tab-separated plain text (by default called `'parallel_conc.txt'`). This file can be opened in MS Excel for further corpus-based analyses.


You can also switch the position of the input corpora. In the example below, the Indonesian text is considered as the source text and the input string in the `pattern` argument of `para_conc()` represents the Indonesian target, keyword.

```{r example-idn-eng}
# in this example, the Indonesian text is used as the source text
my_para_conc <- para_conc(source_text = sci_id, 
                          target_text = sci_en, 
                          pattern = "\\bseharusnya\\b", # regular expression pattern
                          conc_sample = 20) # retrieve 20 random concordance lines
head(my_para_conc)
```


```{r delete-saved-file, echo = FALSE}
unlink("parallel_conc.txt")
```


Here is the R session info for this repository.

```{r sessinfo}
devtools::session_info()
```

